Verifying Demonstrations

### 2018-06-11 paper/SystemModel.tex

For the rest of the paper, we will refer to the organizer as Alice.
Assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul}\footnote{Remark that the objective does not necessarily align with the definition of the police whose interest could be to determine the maximum crowd at any point in time to deploy enough personnel for crowd-control.}.
% cause identifier
\NewVariable{\cid}{cid}
Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.

% protest
\NewVariable{\prtst}{P}
% subprotest
\NewVariable{\sprtst}{p}

@@

% proof share
\NewVariable{\psh}{s}
% proof shares
\NewVariable{\pshs}{S}
% protester identifier
\NewVariable{\pid}{pid}
% witness identifier
\NewVariable{\wid}{wid}

@@

% proof
\NewVariable{\prf}{\pi}
% proofs
\NewVariable{\prfs}{\Pi}

>>>>

For the rest of the paper, we will refer to the organizer as Alice.
Assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul}\footnote{Remark that the objective does not necessarily align with the definition of the police whose interest could be to determine the maximum crowd at any point in time to deploy enough personnel for crowd-control.}.
% cause identifier
Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.

% protest
% subprotest

@@

% proof share
% proof shares
% protester identifier
% witness identifier

@@

% proof
% proofs
